Case study of Scalable Quantum Simulation of Molecular Energies

### 2019-06-21 article.tex
changes
minors change in final section.
add more quotes.

\section{Main Achievement of paper}
As it is known, building a quantum computer comes with many challenges, one being the aspect of scalability. One of the advantages of using PEA to
compute electronic structures of a molecule is better asymptotic scaling which would prove useful for larger molecules than Hydrogen. However, this
is problematic as one would need to utilise more steps in the Trotterisation approximation which would in turn incur higher exponential costs. Hence,
 it was determined that a single Trotter step is not enough to accurately predict chemical rates for a Hydrogen molecule. In addition, for a single
 trotter step, each simulation using PEA was ran using different orderings of local Hamiltonians in order to find the optimal Trotter sequence for
 each bond length. For larger molecules, this is deemed intractable which becomes extremely difficult for the preprocessing requirements for a
 classical computer.

@@

This article is inspired by Scalable quantum simulation of molecular energies \cite{o2016scalable}. Shuhao Yang wrote the Introduction and History sections and the PEA section and box. James Mills wrote the Scientific Background and Conclusion
and Outlook sections and the Experimental Implementation section and box. Shanice St John wrote the Techniques in Paper section introduction and
the Main Achievement of Paper section, and the VQE section and box. However we all edited and redrafted together and interviewed the academics
whose opinions we quoted in the article. We would like to thank Dr Abolfazl Bayat, Prof. Dan Browne and Mikolaj Uryszek for kindly talking to
us and allowing us to quote them here.

>>>>

\section{Main Achievement of paper}
As it is known, building a quantum computer comes with many challenges, one being the aspect of scalability. As the number of qubits increases, it becomes increasingly difficult to solve chemical rates. Senior research fellow Dr Lluis Masanes at University College London commented “Many quantum simulators such as the ion trap give good results but they are not scalable”. Adding more degrees of freedom, becomes computationally challenging and thus impossible to solve classically.

One of the advantages of using PEA to
compute electronic structures of a molecule is better asymptotic scaling which would prove useful for larger molecules than Hydrogen. However, this
is problematic as one would need to utilise more steps in the Trotterisation approximation which would in turn incur higher exponential costs. Hence,
 it was determined that a single Trotter step is not enough to accurately predict chemical rates for a Hydrogen molecule. In addition, for a single
 trotter step, each simulation using PEA was ran using different orderings of local Hamiltonians in order to find the optimal Trotter sequence for
 each bond length. For larger molecules, this is deemed intractable which becomes extremely difficult for the preprocessing requirements for a
 classical computer.

@@

This article is inspired by Scalable quantum simulation of molecular energies \cite{o2016scalable}. Shuhao Yang wrote the Introduction and History sections and the PEA section and box. James Mills wrote the Scientific Background and Conclusion
and Outlook sections and the Experimental Implementation section and box. Shanice St John wrote the Techniques in Paper section introduction and the Main Achievement of Paper section, and the VQE section and box. However we all edited and redrafted together and interviewed the academics
whose opinions we quoted in the article. We would like to thank Dr Abolfazl Bayat, Prof. Dan Browne, Mikolaj Uryszek and Dr Lluis Masanes for kindly talking to
us and allowing us to quote them here.
